Relationships in the extremes and their influence on competition and coexistence

### 2022-03-22 paper/Paper.Rnw
comments + edits for fig 2 script and edits to sexpr callouts in paper fig caption

\begin{figure}
\includegraphics[width=.75\textwidth]{../results_figs/fig2.pdf}
\caption{Our simulated lottery-model populations influenced by asymmetric tail associations (ATAs) recovered 
from low densities less often and 
spent more time in a state of one-species dominance, demonstrating that ATAs can influence aspects of 
species coexistence. Panel (a) shows species 1 from the lottery 
model subject to environmental noise with symmetric tail associations (Fig. \ref{fig:noise}b). Panel (b) shows species 1 from the 
same model with the same parameters, but subject to noise with left-tail association (Fig. \ref{fig:noise}a).
Both simulations were run for \Sexpr{M} time steps, though only the first $1000$ are shown. Periods of 
``noticeable coexistence'' of the species, defined to be periods when each species comprises at least $5\%$ of 
total abundance, are marked in grey. The average duration of periods of noticeable coexistence 
was \Sexpr{fig2$coSym} time steps for panel (a) and \Sexpr{fig2$coATA} for panel (b), over the full length of the simulations; 
whereas the average duration of periods of
one-species dominance was \Sexpr{fig2$domSym} time steps for panel (a) and \Sexpr{fig2$domATA} for (b). Thus, while periods of 
noticeable coexistence were of similar duration for the two scenarios, periods of one-species dominance were much longer,
on average, for the ATA case. Parameters were $\mu_1 = \Sexpr{fig2$params[1] + fig2$params[1]}$,
$\mu_2 = \Sexpr{-(fig2$params[1])}$, $\sigma = \Sexpr{fig2$params[2]}$, and $\delta = \Sexpr{fig2$params[3]}$. 
See Introduction and Fig. \ref{fig:noise} caption for model details. 
\label{fig:pedagog}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=.75\textwidth]{../results_figs/fig2.pdf}
\caption{Our simulated lottery-model populations influenced by asymmetric tail associations (ATAs) recovered 
from low densities less often and 
spent more time in a state of one-species dominance, demonstrating that ATAs can influence aspects of 
species coexistence. Panel (a) shows species 1 from the lottery 
model subject to environmental noise with symmetric tail associations (Fig. \ref{fig:noise}b). Panel (b) shows species 1 from the 
same model with the same parameters, but subject to noise with left-tail association (Fig. \ref{fig:noise}a).
Both simulations were run for \Sexpr{M} time steps, though only the first $1000$ are shown. Periods of 
``noticeable coexistence'' of the species, defined to be periods when each species comprises at least $5\%$ of 
total abundance, are marked in grey. The average duration of periods of noticeable coexistence 
was \Sexpr{fig2$coMets$Sym$co} time steps for panel (a) and \Sexpr{fig2$coMets$Asy$co} for panel (b), over the full length of the simulations; 
whereas the average duration of periods of
one-species dominance was \Sexpr{fig2$coMets$Sym$dom} time steps for panel (a) and \Sexpr{fig2$coMets$Asy$dom} for (b). Thus, while periods of 
noticeable coexistence were of similar duration for the two scenarios, periods of one-species dominance were much longer,
on average, for the ATA case. Parameters were $\mu_1 = \Sexpr{fig2$params[1]$,
$\mu_2 = \Sexpr{fig2$params[2]}$, $\sigma = \Sexpr{fig2$params[3]}$, and $\delta = \Sexpr{fig2$params[4]}$. 
See Introduction and Fig. \ref{fig:noise} caption for model details. 
\label{fig:pedagog}}
\end{figure}
